---
output: rmarkdown::github_document
---
```{r echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  collapse=  TRUE, 
  comment = "##",
  fig.width = 9,
  fig.retina = 2, 
  fig.path = "images/"
)
library("rte.data")
```


# rte.data

> Access data from RTE data portal

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Travis build status](https://travis-ci.org/dreamRs/rte.data.svg?branch=master)](https://travis-ci.org/dreamRs/rte.data)


## Overview

RTE, the french electricity transmission system operator, provides access to various data through an API on its [data portal](https://data.rte-france.com/home). You can retrieve those data with `rte.data`.


Installation (from Github) : 

```{r, eval = FALSE}
source("https://install-github.me/dreamRs/rte.data")

# or
devtools::install_github("dreamRs/rte.data")
```



## Authentication

To access the API, you need to [create an account](https://data.rte-france.com/create_account), or login if you have one.

Once logged, you can subscribe (create an application) to the desired API (each APIs must be subscribed individualy), you'll obtain an `client id` and a `client secret` (or directly a base64 encoded key). Use those to get a token : 

```{r, eval=FALSE}
# To create a token you can use id_client and id_secret
id_client <- "XXXXX-XXXXX-XXXXX-XXXXX-XXXXX"
id_secret <- "XXXXX-XXXXX-XXXXX-XXXXX-XXXXX"
token <- get_token(
  key = list(id_client = id_client, id_secret = id_secret)
)

# or the base64 encoded key
key <- "TGEgZGF0YXNjaWVuY2UgYXZlYyB1biBncmFuZCBS="
token <- get_token(key)
```

With this token, you can query the API. You need to generate a token every ~two hours, but you can use the same key each time.

So for future use, you can store your credentials in your `.Renviron` with `set_key`.


## Examples

### Consumption

Data on French electricity consumption in real time, with forecast :

```{r consumption}
short_term <- get_consumption("short_term", type = c("REALISED", "D-1"))
short_term

autoplot(short_term)
```



### Physical flows

Data about physical cross-border schedules detailing electricity flows actually transiting across the interconnection lines directly linking countries.

```{r balance}
balance <- get_physical_flows(start_date = "2018-02-01", end_date = "2018-03-15")
autoplot(balance)
autoplot(balance, by_country = TRUE)
```



## Actual generation

Generation data aggregated by sector and produced per group (in MW) on an intradaily basis for net generation injected into the network.

```{r generation}
prod_type_30 <- get_actual_generation(
  resource = "actual_generations_per_production_type",
  start_date = Sys.Date() - 30, end_date = Sys.Date()
)

autoplot(prod_type_30, by_day = TRUE)
```



## Active production units 

```{r active-units, fig.height=6}
active_units <- retrieve_active_units()
autoplot(active_units)
```

or see on a map :

```{r active-units-map, fig.height=9}
autoplot(active_units, map = TRUE)
```


## Generation installed capacities

```{r installed-capacities, fig.height=9}
inst_cap <- get_open_api(
  api = "generation_installed_capacities",
  resource = "capacities_per_production_unit"
)

autoplot(inst_cap)
```



